Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/relwk.tex

Nail improves upon Hammer in three ways.  First, Nail generates output in
addition to parsing input.  Second, Nail does not require the programmer
to write potentially insecure semantic actions.  Last, Nail's structural
dependencies and stream transforms allow it to work with protocols that
Hammer cannot handle, such as protocols with offset fields, length fields,
checksums, or compressed data.  (Hammer has limited support for length
fields: it can parse arrays immediately preceded by their length.)

@@

The second class is logic errors, where application code misinterprets
input data. Safe languages and exploit mitigation technologies do not
help against such vulnerabilities. This can lead to serious security
consequences when two systems disagree on the meaning of a network
packet or a signed message.  For example, the XNU kernel in iOS and the
user code-signing verifier interpret executable metadata differently,
so the code signature sees different bytes at a virtual address than the
executable that runs~\cite{evaders6}.  Android's code signing system also
had a vulnerability due to parsing ambiguities~\cite{saurik-masterkey},
and parsing ambiguities even contributed to attacks on the X.509 protocol
underlying SSL~\cite{DBLP:conf/fc/KaminskyPS10}.  Logic errors can also
cause memory corruption bugs as well, for example when a protocol stores
the size of a buffer in two places and the implementation does not check
their consistency. These mistakes are highly application-specific, and
are difficult to mitigate using existing techniques, and these mistakes
can occur even in high-level languages that guarantee memory safety. By
allowing developers to specify their data format just once, Nail avoids
logic errors and inconsistencies in parsing and output generation.

@@

Proper input recognition has been shown to be an excellent way of
eliminating ambiguous inputs.  In one case, a PDF parser (implemented
in Coq) could eliminate over $95\%$ of known malicious PDFs by checking
whether they conform to the PDF format~\cite{Bogk-PDF}. The same project
also produced a ``counter-example'' PDF that triggered numerous bugs
in other PDF parsers. However, manually writing parser code and proving
unambiguity does not scale to the number of file formats and protocols
in existence and might result in parser code tied to one specific
application. By supporting a wide range of real-world file formats,
Nail helps programmers produce precise parsers for complex grammars.

>>>>

Nail improves upon Hammer in three ways.  First, Nail generates output in
addition to parsing input.  Second, Nail does not require the programmer
to write potentially insecure semantic actions.  Last, Nail's structural
dependencies and stream transforms allow it to work with protocols that
Hammer cannot handle, such as protocols with offset fields, length fields,
checksums, or compressed data, although Hammer has special facilities for
arrays immediately preceded by their length.

@@

The second class is logic errors, where application code misinterprets
input data. Safe languages and exploit mitigation technologies do not
help against such vulnerabilities. This can lead to serious security
consequences when two systems disagree on the meaning of a network
packet or a signed message.  For example, the XNU kernel in iOS and the
user-mode code-signing verifier interpret executable metadata differently,
so the code signature sees different bytes at a virtual address than the
executable that runs~\cite{evaders6}.  Android's code signing system also
had a vulnerability due to parsing ambiguities~\cite{saurik-masterkey},
and parsing ambiguities even contributed to attacks on the X.509 protocol
underlying SSL~\cite{DBLP:conf/fc/KaminskyPS10}.  Logic errors can also
cause memory corruption bugs as well, for example when a protocol stores
the size of a buffer in two places and the implementation does not check
their consistency. These mistakes are highly application-specific, and
are difficult to mitigate using existing techniques, and these mistakes
can occur even in high-level languages that guarantee memory safety. By
allowing developers to specify their data format just once, Nail avoids
logic errors and inconsistencies in parsing and output generation.

@@

Proper input recognition has been shown to be an excellent way of
eliminating ambiguous inputs.  In one case, a PDF parser (implemented
in Coq) rejects over $95\%$ of known malicious PDFs by checking
whether they conform to the PDF format~\cite{Bogk-PDF}. The same project
also produced a ``counter-example'' PDF that triggered numerous bugs
in other PDF parsers. However, manually writing parser code and proving
unambiguity does not scale to the number of file formats and protocols
in existence and might result in parser code tied to one specific
application. By supporting a wide range of real-world file formats,
Nail helps programmers produce precise parsers for complex grammars.
